### 2020-08-28 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.08,409.37) --
	(106.21,409.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.51,401.22) --
	( 98.51,415.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.51,406.14) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.95,474.99) --
	(188.09,474.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.83,473.08) --
	(184.83,476.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.83,470.96) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.65,474.30) --
	(102.96,474.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.44,471.52) --
	( 98.44,476.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.44,470.27) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.75,424.33) --
	( 97.88,424.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.70,416.17) --
	( 92.70,430.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.70,420.29) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.46,386.96) --
	(113.76,386.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.13,378.15) --
	(104.13,393.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.13,384.05) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.32,483.57) --
	(194.53,483.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.94,482.97) --
	(193.94,484.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.94,480.66) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.20,470.80) --
	(170.02,470.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.66,467.68) --
	(168.66,473.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.66,467.57) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.39,475.00) --
	(191.75,475.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.60,470.62) --
	(187.60,478.61);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,470.96) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.47,480.80) --
	(187.89,480.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.19,478.95) --
	(187.19,482.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.19,476.77) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.19,457.78) --
	(173.69,457.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.12,454.35) --
	(171.12,460.71);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.12,453.74) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,460.59) --
	(174.27,460.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,456.85) --
	(173.11,463.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,457.69) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,485.03) --
	(197.77,485.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.24,483.39) --
	(196.24,486.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.24,482.13) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.67,442.74) --
	(172.67,448.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.67,442.37) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.04,481.91) --
	(199.30,481.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.99,481.15) --
	(195.99,482.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.99,477.88) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,483.17) --
	(201.19,483.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.73,482.87) --
	(194.73,483.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,479.14) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.61,413.21) --
	(141.61,424.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.61,415.90) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.98,435.47) --
	(171.98,440.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.98,435.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.52,487.53) --
	(197.96,487.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.74,487.09) --
	(197.74,487.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,484.63) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.67,450.29) --
	(147.06,450.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.14,448.74) --
	(142.14,451.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.14,447.06) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.48,480.63) --
	(196.33,480.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.61,479.97) --
	(193.61,481.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,476.60) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,479.97) --
	(184.03,479.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.70,479.64) --
	(181.70,480.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.70,475.94) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.78,442.10) --
	(143.02,442.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.16,440.36) --
	(138.16,443.70);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.16,438.06) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.72,440.69) --
	(144.81,440.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.64,439.60) --
	(139.64,441.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.64,437.78) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.55,488.06) --
	(198.21,488.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.88,487.69) --
	(197.88,488.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.88,485.15) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (123.29,429.70) --
	(134.35,429.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.55,425.74) --
	(129.55,433.02);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.55,426.47) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,475.22) --
	(196.89,475.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.22,472.58) --
	(190.22,477.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.22,471.19) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,475.58) --
	(153.58,475.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.65,474.36) --
	(152.65,476.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.65,471.55) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.83,424.98) --
	(122.98,424.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.72,420.83) --
	(119.72,428.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.72,420.95) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.22,406.71) --
	(136.61,406.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.44,404.17) --
	(132.44,408.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.44,403.80) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.61,485.43) --
	(196.23,485.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.92,484.44) --
	(195.92,486.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.92,482.52) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.63,453.48) --
	(167.63,460.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.63,454.02) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.33,472.88) --
	(196.07,472.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.27,470.47) --
	(182.27,475.03);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.27,468.84) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.68,480.81) --
	(208.94,480.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.36,480.47) --
	(203.36,481.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.36,476.77) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.51,449.17) --
	(188.52,449.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.77,446.85) --
	(176.77,451.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.77,445.14) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.26,455.28) --
	(183.26,459.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.26,454.41) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.59,486.76) --
	(197.77,486.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.19,486.27) --
	(197.19,487.23);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.19,483.85) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.42,469.49) --
	(156.55,469.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.93,468.42) --
	(143.93,470.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.93,466.26) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.45,480.12) --
	(196.70,480.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.33,479.27) --
	(184.33,480.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.33,476.09) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.84,479.79) --
	(170.18,479.79);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:28:47
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,403.16) --
	(175.00,578.16);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,477.44) --
	(  0.00,175.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,365.13) --
	(213.03,578.16);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,515.47) --
	(  0.00,213.03);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,327.11) --
	(251.05,578.16);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (302.44,578.16) --
	(302.44,553.49) --
	(  0.00,251.05);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,464.39) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.36) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,388.34) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.41,410.95) --
	( 91.01,410.95);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.43,396.47) --
	( 85.43,420.38);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.43,407.72) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.48,467.57) --
	(182.33,467.57);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.56,466.01) --
	(179.56,469.05);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.56,463.54) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.27,472.87) --
	( 87.83,472.87);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.75,471.19) --
	( 84.75,474.46);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.75,468.84) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.34,424.98) --
	( 96.67,424.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 88.68,419.14) --
	( 88.68,429.79);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 88.68,420.94) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.52,382.73) --
	(108.13,382.73);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 96.89,359.01) --
	( 96.89,395.26);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 96.89,379.83) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.26,478.14) --
	(189.63,478.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.95,477.37) --
	(188.95,478.88);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.95,475.23) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.10,467.30) --
	(170.92,467.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.88,465.91) --
	(159.88,468.61);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.88,464.07) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.80,474.02) --
	(190.74,474.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.02,472.32) --
	(185.02,475.62);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.02,469.99) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.73,476.99) --
	(183.11,476.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.67,476.82) --
	(179.67,477.16);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.67,472.96) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.34,449.32) --
	(177.09,449.32);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.26,447.98) --
	(164.26,450.60);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.26,445.29) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.89,454.32) --
	(191.13,454.32);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.96,452.70) --
	(173.96,455.85);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.96,451.42) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.24,481.37) --
	(192.56,481.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.42,480.81) --
	(191.42,481.92);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.42,478.46) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.68,424.45) --
	(151.68,434.52);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.68,426.72) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.78,476.44) --
	(192.59,476.44);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.44,475.09) --
	(184.44,477.73);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.44,472.41) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.84,478.90) --
	(189.05,478.90);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.62,478.65) --
	(183.62,479.14);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.62,474.86) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.64,389.28) --
	(148.64,395.86);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.64,388.74) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.92,416.68) --
	(159.92,425.68);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.92,418.64) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.20,483.88) --
	(195.50,483.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.86,483.48) --
	(194.86,484.29);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.86,480.98) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.50,437.03) --
	(144.50,441.13);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.50,435.93) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.76,476.35) --
	(192.56,476.35);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.59,475.11) --
	(182.59,477.54);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.59,472.32) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.54,475.45) --
	(177.27,475.45);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.14,475.33) --
	(169.14,475.58);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.14,471.42) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.49,430.50) --
	(142.49,432.37);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.49,427.42) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.23,425.41) --
	(160.23,429.48);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.23,424.62) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.33,484.64) --
	(195.61,484.64);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.98,484.32) --
	(194.98,484.95);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.98,481.73) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.54,432.34) --
	(123.04,432.34);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.35,429.11) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.64,471.96) --
	(192.30,471.96);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.87,467.92) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.95,472.27) --
	(142.09,472.27);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.90,468.23) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.73,415.23) --
	(106.54,415.23);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.06,411.19) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.15,400.30) --
	(118.93,400.30);
\definecolor{drawColor}{RGB}{0,219,171}
